Analyzing Information Transfer from Different Data Sources via Precise Bias-variance Asymptotics

### 2021-07-08 revision_journal/intro.tex
sec 4 wip

On the other hand, the bias limit is much harder to study, and its exact dependence on the sample ratio and the covariate shift matrix is still an open problem in random matrix theory in the most general setting. However, when the data is Gaussian distributed and there is no covariante shift, we can use recent results in \cite{BES_free1,BES_free2} to derive the bias limit. To the best of our knowledge, we are not aware of any previous result in the high-dimensional setting, even for two sample covariance matrices with isotropic population covariances and the same sample size.

>>>>

On the other hand, the bias limit is much harder to study, and its dependence on the sample ratio and the covariate shift is still an open problem in random matrix theory in the most general setting. However, when the data is Gaussian distributed and the two tasks have the same population covariance, we find a way to calculate the exact bias limit using free probability techniques. Leveraging on the recent results \cite{BES_free1,BES_free2}, we can obtain a sharp convergence rate to the bias limit. To the best of our knowledge, we are not aware of any previous result on the precise bias limit in the high-dimensional setting, even for two Wishart matrices with the same sample size.

### 2021-07-08 revision_journal/multitask.tex
reorg wip
update intro wip
Updates from Overleaf
sec 4 wip

\section{Asymptotics for Multiple Tasks}\label{sec_same}

@@

Hard parameter sharing is a commonly used architecture in multi-task learning. However, there have been few theoretical results on the performance of the HPS estimators in high-dimensional multi-task learning. In this section, we extend our results on the predication loss of the HPS estimator to a multi-task linear regression, where all tasks have the same covariates. We make this extension for the following reasons. First, its restriction to the two-task case provides a rare example where the output layers $A_1$ and $A_2$ can be characterized exactly. Second, the proof of the multi-task case is no harder than the two-task case, but it can provide much clearer geometric intuition  as we will discuss below. Third, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}. Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
%It is not hard to extend the above result to the cases with more than two tasks. {\cor For the general case, we study them in a future work.}

@@

\vspace{5pt}
\noindent\textbf{Multi-task setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$. The label vector of the $i$-th task follows a linear model
$$Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)},\quad i=1,2,\cdots, t.$$
We assume that $X=Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}, that is, $Z$ is an $n\times p$ random matrix with i.i.d. entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}. $\varepsilon^{(i)} \in \real^{n}$, $i=1,2,\cdots, t$, are independent random vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}. Finally, $X$, $\ve^{(i)}$ and $\beta^{(i)}$, $i=1,2,\cdots, t$, are all  independent from each other.

\begin{figure*}[!t]
	\centering
	\includegraphics[width=0.3\textwidth,valign=t]{figures/mtl_model_arch.pdf}
	\caption{A hard parameter sharing architecture}
	\label{fig_intro_arch}
\end{figure*}
%\begin{enumerate}
%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
%\end{enumerate}

	To define the HPS parameter for the above setting, we study the following minimization problem % \eqref{eq_tsl} becomes
	\begin{align}
		f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
	\end{align}
	where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$. %Recall that $r$ is the width of $B$.
We will focus on cases with $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).

	%If $r\ge t$, then it is trivial to observe that we can always choose the parameters $A$ and $B$ such that $BA_i$ can fit any parameter $\beta^{(i)}\in \R^p$, which leads to a vanishing predication loss. Hence we only consider the case with $r<t$. \FY{Correct it if the reason is wrong.}

	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
	\begin{align}
		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
	\end{align}
	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
	\begin{align}\label{eq_mtl_output_layer}
		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
	\end{align}
%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$.
Let $\hat A$ be the global minimizer of $g(A)$. Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$. We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in
and its (out-of-sample) prediction loss as
\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee

Our main result of this section, Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace. To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which can be regarded as the covariance of the task labels):
\begin{align}\label{eq_A_star}
	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
\end{align}
where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices.
 To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue. Otherwise, $A^{\star}$ is not well-defined and Theorem \ref{thm_many_tasks} will give a null result.
 %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction. Then we have the following result.

@@

\begin{theorem}\label{thm_many_tasks}
%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant. Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}. Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
	%Let $n = c \cdot p$.
	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
	%that satisfy Assumption \ref{assm_secA2} in the appendix.
	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}.
Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary (small) constant. Then for any task $i = 1,  \cdots, t$, we have that with high probability,
\be\label{minimizer_beta}
\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
\ee
where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$. Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that  with high probability,
	\begin{align}
		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right). \label{Li_multi1}
		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
	\end{align}
	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$. %and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
Finally, we have a better bound for the averaged prediction loss:  with high probability,
\begin{align}
&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
 &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 .\label{Li_multi2}
\end{align}

\end{theorem}

@@

The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}. Moreover, by setting $t=2$ in Theorem \ref{thm_many_tasks}, we can obtain the prediction loss for the HPS estimator for the transfer learning setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$. For the reader's convenience, we give the precise statement in Corollary \ref{thm_two_tasks}.
%Theorem \ref{thm_many_tasks} implies Theorem \ref{thm_two_tasks} as a special case with $t=2$ and $r=1$.
%In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix
$ {B^\star}^\top \Sigma  B^\star,$ where recall that $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ by definition.
% is the matrix formed by the linear model parameters of the two tasks.
Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is uniquely defined. %Otherwise, Theorem \ref{thm_two_tasks} will give a null result.
In the following corollary, the estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.

\begin{corollary}\label{thm_two_tasks}
Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2\equiv n$. Let $c>0$ be an arbitrary (small) constant. Then we have that with high probability,
\be\label{minimizer_beta1}
\left\| u_{\hat a}u_{\hat a}^\top - A^\star {A^\star}^\top\right\|_F  \le  \left[\frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_1 - \lambda_{2} } \right]^{1/2},
\ee
where $u_{\hat a}$ is the unit vector defined as
$ u_{\hat a}:= \frac1{\hat a^2 +1} \begin{pmatrix} {\hat a}\\ 1\end{pmatrix},$ and $\lambda_1 $ and $\lambda_{2}$ are respectively the larger and smaller eigenvalues of ${B^\star}^\top\Sigma B^\star$.
%for task 2,  % over the randomness of the input,
Moreover, the prediction loss of the HPS estimator satisfies that with high probability,
	\begin{align}
		& \bigabs{L_2(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) \cdot B^{\star}A^{\star}  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
		& \le  \left[  \frac{  n^{-1/2+2/\varphi+c} \|{B^{\star}}^{\top}\Sigma B^{\star}\|+n^{-1/2+c} \sigma^2} {\lambda_1  - \lambda_2 }\right]^{1/2}   \left(\norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2\right), \label{Li_multi0}
		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
	\end{align}
	 where $A^\star(2)$ denotes the second entry of $A^\star$.
	 \end{corollary}

\paragraph{Examples.}
Obviously, the concentration error decreases with $n$.
First, we consider the variance of $\hat{\beta}_i^{\MTL}$, which is $\sigma^2\norm{a_i^{\star}} \bigtr{\Sigma (X^{\top} X)^{-1}}$?
It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.

>>>>

\section{Extension to multiple data sources}\label{sec_same}

@@

%Hard parameter sharing is a commonly used architecture in multi-task learning. However, there have been few theoretical results on the performance of the HPS estimators in high-dimensional multi-task learning. In this section, we extend our results on the predication loss of the HPS estimator to a multi-task linear regression, where all tasks have the same covariates. We make this extension for the following reasons. First, its restriction to the two-task case provides a rare example where the output layers $A_1$ and $A_2$ can be characterized exactly. Second, the proof of the multi-task case is no harder than the two-task case, but it can provide much clearer geometric intuition  as we will discuss below. Third, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}. Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
%It is not hard to extend the above result to the cases with more than two tasks. {\cor For the general case, we study them in a future work.}

@@

Our setup and the results in Section \ref{sec_main} are both for transferring from one data source.
This section extends our setup to transfer learning from multiple data sources.
We focus on a natural setting where all the tasks have the same covariates but different labels.

\paragraph{Data model.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$. The label vector of the $i$-th task follows a linear model
\begin{align}
    Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)}, \text{ for } i=1, 2,\cdots, t.
\end{align}
We assume several standard conditions on $X$ and each of $\varepsilon^{(i)}$.
First, $X = Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}.
%that is, $Z$ is an $n\times p$ random matrix with i.i.d. entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}.
Second, every $\varepsilon^{(i)} \in \real^{n}$ is a random vector with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in equation \eqref{eq_highmoments}.
Finally, $\beta^{(i)} \in \real^{p}$ is a fixed vector independent from the other linear models, the feature covariates, and all noise vectors.

%\begin{figure*}[!t]
%	\centering
%	\includegraphics[width=0.3\textwidth,valign=t]{figures/mtl_model_arch.pdf}
%	\caption{A hard parameter sharing architecture}
%	\label{fig_intro_arch}
%\end{figure*}
%\begin{enumerate}
%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
%\end{enumerate}

\paragraph{Estimator.} We extend the two-layer linear neural network from equation \eqref{eq_hps} to combine multiple data sources as follows:
\begin{align}
	f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
\end{align}
where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$. %Recall that $r$ is the width of $B$.
We will focus on cases with $r < t$.
Otherwise, the global minimum of $f(A, B)$ reduces to single-task learning, similar to Proposition \ref{prop_large_r} (details omitted).

Let $\hat A$ be the global minimizer of $g(A)$. Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$. We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in
and its (out-of-sample) prediction loss as
\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee

	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
	\begin{align}
		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
	\end{align}
	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
	\begin{align}\label{eq_mtl_output_layer}
		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
	\end{align}
%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$.

\paragraph{Result.} Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace. To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which can be regarded as the covariance of the task labels):
\begin{align}\label{eq_A_star}
	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
\end{align}
where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices.
 To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue. Otherwise, $A^{\star}$ is not well-defined and Theorem \ref{thm_many_tasks} will give a null result.
 %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction. Then we have the following result.

@@

\begin{theorem}\label{thm_many_tasks}
%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant. Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}. Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
	%Let $n = c \cdot p$.
	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
	%that satisfy Assumption \ref{assm_secA2} in the appendix.
	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}.
Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary (small) constant. Then for any task $i = 1,  \cdots, t$, we have that with high probability,
\be\label{minimizer_beta}
\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
\ee
where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$. Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that  with high probability,
	\begin{align}
		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right). \label{Li_multi1}
		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
	\end{align}
	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$. %and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
Finally, we have a better bound for the averaged prediction loss:  with high probability,
\begin{align}
&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
 &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 .\label{Li_multi2}
\end{align}
\end{theorem}

@@

The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}.

\begin{figure*}[!t]
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/same_covariates.eps}
		\caption{Example \ref{ex_same_cov}}
		\label{fig_same_cov}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/same_covariates.eps}
		\caption{Example \ref{ex_sample_ratio}}
		\label{fig_width}
	\end{subfigure}
%	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
%	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
%	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
%	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
%	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
%	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
%	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one. Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
%	\label{fig_model_shift_phasetrans}
\end{figure*}

%Moreover, by setting $t=2$ in Theorem \ref{thm_many_tasks}, we can obtain the prediction loss for the HPS estimator for the transfer learning setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$. For the reader's convenience, we give the precise statement in Corollary \ref{thm_two_tasks}.
%Theorem \ref{thm_many_tasks} implies Theorem \ref{thm_two_tasks} as a special case with $t=2$ and $r=1$.
%In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
%We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix
%$ {B^\star}^\top \Sigma  B^\star,$ where recall that $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ by definition.
% is the matrix formed by the linear model parameters of the two tasks.
%Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is uniquely defined. %Otherwise, Theorem \ref{thm_two_tasks} will give a null result.
%In the following corollary, the estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
